---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# weathervane

```{r, echo = FALSE}
description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
min.r <- substr(description[,"Depends"], 7, 11)
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![Package version](https://img.shields.io/badge/Package%20version-`r version`-80b6ff.svg)](/DESCRIPTION)
[![R dependency](https://img.shields.io/badge/R%3E%3D-`r min.r`-80b6ff.svg)](https://cran.r-project.org/)
[![R-CMD-check](https://github.com/biometryhub/weathervane/workflows/R-CMD-check/badge.svg)](https://github.com/biometryhub/weathervane/actions)
[![Codecov test coverage](https://codecov.io/gh/biometryhub/weathervane/branch/main/graph/badge.svg)](https://codecov.io/gh/biometryhub/weathervane?branch=main)
[![Hits](https://hits.seeyoufarm.com/api/count/incr/badge.svg?url=https%3A%2F%2Fbiometryhub.github.io%2Fweathervane%2F&count_bg=%2379C83D&title_bg=%23555555&icon=&icon_color=%23E7E7E7&title=hits&edge_flat=false)](https://hits.seeyoufarm.com)
<!-- badges: end -->

Easily navigate and retrieve weather datasets for anywhere in Australia!

The **weathervane** package aids researchers in retrieving Australian weather 
and climate data (sourced from SILO and the Bureau of Meteorology) to 
incorporate into statistical analyses of agronomic experiments and 
plant-breeding trials.

# Installation

Run the following code on your R console to install this package:

```{r install, eval = FALSE}
if(!require("remotes")) install.packages("remotes") 
remotes::install_github("biometryhub/weathervane", upgrade = FALSE)
```

# Using the package

Load the package and start using it with:

```{r load, eval = F}
library(weathervane)
```

TODO more here

# Attribution to SILO/Bureau of Meteorology
The weather datasets currently retrieved by **weathervane** are curated by
[SILO](https://www.longpaddock.qld.gov.au/silo/),
who make them available under a Creative Commons Attribution 4.0
International Licence. Their data is in turn mostly sourced from the
[Australian Bureau of Meteorology](http://www.bom.gov.au/) and
their weather stations.
  
Please reference them appropriately in any publications or
other research outputs that use the downloaded weather data. 
See for example:
- https://www.longpaddock.qld.gov.au/silo/about/access-data/

- http://www.bom.gov.au/other/copyright.shtml

