---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# weathervane

```{r, echo = FALSE}
description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
min.r <- substr(description[,"Depends"], 7, 11)
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![R version](https://img.shields.io/badge/weathervane.R%20version-0.1.0-80b6ff.svg)](/weathervane.R)
[![R dependency](https://img.shields.io/badge/R%3E%3D-`r min.r`-80b6ff.svg)](https://cran.r-project.org/)
[![R-CMD-check](https://github.com/biometryhub/weathervane/workflows/R-CMD-check/badge.svg)](https://github.com/biometryhub/weathervane/actions)
<!-- badges: end -->

The mythical 'Australia weather App' that automates retrieving weather data. Finally getting around to finishing it.

### 13/08/2021
Update/finalising. At some point document here the three ways to use
weathervane (e.g. the R package, the Shiny App or the ruby CLI interface).
Alternatively perhaps remove the Ruby version later? (e.g. if we're preparing
for CRAN or something?)
